Distinction Centrality Analysis

### 2025-07-31 analysis.qmd
a bucha

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) #circle graph
   g11 <- delete_vertices(g11, 8) #path graph
```

```{r Toy Networks Plots}
   source(here("Functions", "plot.graph.norm.R"))
   png(here("Plots", "Toys", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "path.png"))
   plot.graph.norm(g11, l = "kk")
   dev.off()
```

>>>>

```{r Toy Examples}
   source(here("Functions", "distinction.R"))
   g1 <- make_star(7, mode = "undirected") # star graph
   distinction(g5, norm = "eig")
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) 
   g11 <- delete_vertices(g11, 8) #path graph
   source(here("Functions", "distinction.R"))
   all.dis <- function(x) {
      distinct <- list()
      distinct[[1]] <- distinction(x)
      distinct[[2]] <- distinction(x, norm = "one")
      distinct[[3]] <- distinction(x, norm = "eig")
      return(distinct)
      }
   all.dis(g9)
```

```{r Bonacich examples}
   g13 <- make_empty_graph(10, directed = FALSE)
   g13 <- g13 + edge(1,2)
   g13 <- g13 + edge(1,3)
   g13 <- g13 + edge(1,9)
   g13 <- g13 + edge(2,3)
   g13 <- g13 + edge(2,10)
   g13 <- g13 + edge(3,4)
   g13 <- g13 + edge(4,5)
   g13 <- g13 + edge(4,6)
   g13 <- g13 + edge(5,10)
   g13 <- g13 + edge(5,6)
   g13 <- g13 + edge(6,7)
   g13 <- g13 + edge(7,8)
   g13 <- g13 + edge(7,9)
   g13 <- g13 + edge(8,10)
   g13 <- g13 + edge(8,9) #Bonacich (2007) regular network Fig. 5
   g14 <- make_empty_graph(12, directed = FALSE)
   g14 <- g14 + edge(1,2)
   g14 <- g14 + edge(1,6)
   g14 <- g14 + edge(1,7)
   g14 <- g14 + edge(2,3)
   g14 <- g14 + edge(2,10)
   g14 <- g14 + edge(3,4)
   g14 <- g14 + edge(3,8)
   g14 <- g14 + edge(4,5)
   g14 <- g14 + edge(4,11)
   g14 <- g14 + edge(5,6)
   g14 <- g14 + edge(5,9)
   g14 <- g14 + edge(6,12)
   g14 <- g14 + edge(7,8)
   g14 <- g14 + edge(7,9)
   g14 <- g14 + edge(8,9)
   g14 <- g14 + edge(10,11)
   g14 <- g14 + edge(10,12)
   g14 <- g14 + edge(11,12)
```

```{r Estrada examples}
   g15 <- make_empty_graph(8, directed = FALSE)
   g15 <- g15 + edge(1,2)
   g15 <- g15 + edge(1,5)
   g15 <- g15 + edge(1,8)
   g15 <- g15 + edge(2,3)
   g15 <- g15 + edge(2,8)
   g15 <- g15 + edge(3,4)
   g15 <- g15 + edge(3,6)
   g15 <- g15 + edge(4,5)
   g15 <- g15 + edge(4,7)
   g15 <- g15 + edge(5,6)
   g15 <- g15 + edge(6,7)
   g15 <- g15 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
   g16 <- make_full_graph(9, directed = FALSE)
   g16 <- g16 - edge("1|6")
   g16 <- g16 - edge("1|5")
   g16 <- g16 - edge("2|4")
   g16 <- g16 - edge("2|9")
   g16 <- g16 - edge("3|6")
   g16 <- g16 - edge("3|8")
   g16 <- g16 - edge("4|7")
   g16 <- g16 - edge("5|8")
   g16 <- g16 - edge("7|9") #Fig 1(b) https://doi.org/10.1103/PhysRevE.71.056103
```

```{r Toy Networks Plots}
   source(here("Functions", "distinction.R"))
   source(here("Functions", "plot.graph.norm.R"))
   png(here("Plots", "Toys", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "path.png"))
   plot.graph.norm(g11, l = "kk")
   dev.off()
   source(here("Functions", "plot.graph.cat.R"))
   png(here("Plots", "Toys", "bonacich1.png"))
   plot.graph.cat(g13, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "bonacich2.png"))
   plot.graph.cat(g14, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "estrada1.png"))
   plot.graph.cat(g15, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "estrada2.png"))
   plot.graph.cat(g16, l = "circle")
   dev.off()
```
